Batch, Off-Policy Apprencticeship Learning

### 2011-03-28 main.tex
Modifié ma section pour coller à ce que MAtthieu a écrit

\section{Background}
A sequential decision problem is often framed as a Markov Decision
Process (MDP)~\citep{puterman1994markov}. A MDP is a tuple
$\{S,A,P,R,\gamma\}$ with $S$ being the state space, $A$ the action
space, $P\in\mathcal{P}(S)^{S\times A}$ the set of Markovian
transition probabilities, $R\in\mathbb{R}^S$ the reward function
(assumed to be absolutely bounded by 1) and $\gamma\in[0,1[$ a
discounting factor. A policy $\pi\in A^S$ maps states to action. The
quality of a policy is quantified by the associated value function
$V^\pi$, which associates to each state the expected and discounted
cumulative reward:
\begin{equation}
  V^\pi(s) = E[\sum_{t=0}^\infty \gamma^t R(s_t)|s_0=s, \pi]
\end{equation}
Dynamic programming aims at finding the optimal policy $\pi^*$, that
is one of the policies associated to the optimal value function,
$V^* = \argmax_\pi V^\pi$, which maximizes the value for each state.
If the model (that is transition probabilities and the reward
function) is unknown, learning the optimal control through
interactions is addressed by reinforcement learning.

@@

We assume that the true reward function belongs to some hypothesis
space $\mathcal{H}_\phi = \{\theta^T \phi(s),
\theta\in\mathbb{R}^p\}$, of which we assume the basis functions to
be bounded by 1: $|\phi_i(s)|\leq 1, \forall s\in S, 1\leq i \leq
p$. Therefore, there exists a parameter vector $\theta^*$ such that:
\begin{equation}
  R^*(s) = (\theta^*)^T \phi(s)
\end{equation}
In order to ensure that rewards are bounded, we impose that
$\|\theta\|_2\leq 1$. For any reward function belonging to
$\mathcal{H}_\phi$ and for any policy $\pi$, the related value
function $V^\pi(s)$ can be expressed as follows:
\begin{align}
  V^\pi(s) &= E[\sum_{t=0}^\infty \gamma^t \theta^T \phi(s_t)|s_0=s, \pi]
  \\
  &= \theta^T  E[\sum_{t=0}^\infty \gamma^t \phi(s_t)|s_0=s, \pi]
\end{align}
Therefore, the value function is also linearly parameterized, with
the same weights and with basis functions being grouped into the
so-called \emph{feature expectation} $\mu^\pi$:
\begin{equation}
  \mu^\pi(s) = E[\sum_{t=0}^\infty \gamma^t \phi(s_t)|s_0=s, \pi]
\end{equation}
Recall that the problem is to find a policy whose performance is
close to that of the expert's for the starting state $s_0$, on the
unknown reward function $R^*$. In order to achieve this goal, it is
proposed in~\citep{abbeel2004apprenticeship} to find a policy $\tilde{\pi}$ such
that $\|\mu^{\pi_E}(s_0)-\mu^{\tilde{\pi}}(s_0)\|_2\leq \epsilon$
for some (small) $\epsilon>0$. Actually, this ensures that the value
of the expert's policy and the value of the estimated policy (for
the starting state $s_0$) are close for \emph{any} reward function
of $\mathcal{H}_\phi$:
\begin{align}
  |V^{\pi_E}(s_0) - V^{\tilde{\pi}}(s_0)| &=
  |\theta^T(\mu^{\pi_E}(s_0)-\mu^{\tilde{\pi}}(s_0))|
  \\
  &\leq \|\mu^{\pi_E}(s_0)-\mu^{\tilde{\pi}}(s_0)\|_2
\end{align}
This last equation uses the Cauchy-Schwartz inequality and the
assumption that $\|\theta\|_2\leq 1$. Therefore, the approach
described here does not ensure to retrieve the true reward function
$R^*$, but to act as well as the expert under this reward function
(and actually under any reward function, notably the unknown optimal
one).

@@

\section{LSTD-$\mu$}
Let us write the definition of the $i^\text{th}$ component of a
feature expectation $\mu^\pi(s)$ for some policy $\pi$:
\begin{equation}
  \mu_i^\pi(s) = E[\sum_{t=0}^\infty \gamma^t \phi_i(s_t)|s_0=s,\pi]
\end{equation}
This is exactly the definition of the value function of the policy
$\pi$ for the MDP considered with the $i^\text{th}$ basis function
$\phi_i(s)$ as the reward function. There exists many algorithms to
estimate a value function, any of them can be used to estimate
$\mu_i^\pi$. Based on this remark, we propose to use specifically
the least-squares temporal difference (LSTD)
algorithm~\citep{bradtke1996linear} to estimate each component of the
feature expectation (as each of these components can be understood
as a value function related to a specific and known reward
function).

Assume that a set of transitions $\{(s_t,r_t,s_{t+1})_{1\leq t \leq
n}\}$ sampled according to the policy $\pi$ is available. We assume
that value functions are searched for in some  hypothesis space
$\mathcal{H}_\psi = \{ \hat{V}_\xi(s) = \sum_{i=1}^q \xi_i \psi_i(s)
= \xi^T \psi(s), \xi\in\mathbb{R}^q\}$. As reward and value
functions are possibly quite different, another hypothesis space is
considered for value function estimation. But if $\mathcal{H}_\phi$
is rich enough, one can still consider
$\mathcal{H}_\psi=\mathcal{H}_\phi$. Therefore, we are looking for
an approximation of the following form:
\begin{equation}
  \hat{\mu}_i^\pi(s) = (\xi_i^*)^T \psi(s)
\end{equation}
The parameter vector $\xi_i^*$ is here the LSTD estimate:
\begin{equation}
  \xi_i^* = \left(\sum_{t=1}^n
  \psi(s_t)(\psi(s_t)-\gamma\psi(s'_{t}))^T\right)^{-1}
  \sum_{t=1}^n \psi(s_t) \phi_i(s_t)
\end{equation}
For apprenticeship learning, we are interested more particularly in
$\hat{\mu}^\pi(s_0)$. Let $\Psi = (\psi_i(s_t))_{t,i}$ be the
$n\times q$ matrix of values predictors, $\Delta\Psi = (\psi_i(s_t)
- \gamma\psi_i(s'_t))_{t,i}$ be the related $n\times q$ matrix and
$\Phi = (\phi_i(s_t))_{t,i}$ the $n\times p$ matrix of reward
predictors. It can be easily checked that $\hat{\mu}^\pi(s_0)$
satisfies:
\begin{equation}
  (\hat{\mu}^\pi(s_0))^T = \psi(s_0)^T (\Psi^T \Delta\Psi)^{-1} \Psi^T \Phi
\end{equation}
This provides an efficient way to estimate the feature expectation
of the expert in $s_0$.

@@

\section{Experimental benchmark}
\label{sec:exp}
The experimental benchmark chosen here is the same as in \citep{ng2000algorithms}, a 5x5 grid world. The agent is in one of the case of the grid (whose coordinates is the state) and can choose at each step one of the four compass directions (the action). With probability 0.9, the agent moves in the intended direction. With probability 0.1, the direction is randomly drawn (and thus have probability 0.25 to match the original direction). The reward optimized by the expert is 0 everywhere but in the upper-right square, where it is 1. For every policy, an episodes ends when the upper right square is attained, or after 20 steps. At the start of each episode, the agent is in the lower-left corner of the grid (the opposite of where the reward is).\\

Both the state and action spaces are finite and of small cardinality. Hence, the chosen feature functions $\phi$ and $\psi$ (see section \ref{sec:back}) are the typical features of a tabular representation : 0 everywhere but at a given index $i$ for which the value is 1. There is a bijective mapping from the input space elements ($S$ for $\psi$, $S \times A$ for $\phi$) to the indexes $i$ for which the coordinate of the feature is 1.\\

Both \citet{abbeel2004apprenticeship}'s algorithm (mc\_ANIRL) and our adaptation (lstd\_ANIRL) are tested side by side. The pseudo code of the implementation we used can be found figure \ref{fig:alg}.\\

The MDP solver of mc\_ANIRL is LSPI with a (very) big matrix $D$ as a sample source. $\mu_\pi(s_0)$ and $\mu_E(s_0)$ are computed thanks to a (very) big Monte-Carlo estimation. Both these computations are  as good as perfect theoretical solvers for all intended purpose on this toy problem. We thus are in the case intended by \citet{abbeel2004apprenticeship}.\\

On the other hand lstd\_ANIRL is used as if it could not have access to the simulator. It uses LSPI and LSTD$\mu$, fed only with the expert's transitions. This corresponds to a real-life setting where data generation is expensive and the system can not be controlled by an untrained machine.\\

We want to compare the porformance of both versions of the algorithm with repect to the number of samples available from the expert, as these samples usually are the bottleneck. The discussion about the choice of the performance metric has its own dedicated section (section \ref{sec:perf}). We use here the $||\mu(s_0) - \mu_E(s_0)||_2$ error term.\\

Figure \ref{fig:E} shows, for some numbers of samples from the expert, the value of $||\mu(s_0)-\mu_E(s_0)||_2$ after the algorithm converged or attained the maximum number of iterations (we used 40). The best policy is found by lstd\_ANIRL after one iteration only (this is being investigated), whereas in mc\_ANIRL convergence happens after at least ten iterations, and the best policy is not always the last. The score of the best policy (not the last) is what is plotted here.\\

We can see that although lstd\_ANIRL is not as good as mc\_ANIRL when very few samples are available, both algorithm quickly converge to almost the same value (we don't know yet if the seemingly slightly better performance of lstd\_ANIRL is an artifact). The fact that lstd\_ANIRL can work in a batch, off-policy and model-free setting, while requesting less computing power than mc\_ANIRL makes it suitable to a range of task inaccessible to the mc\_ANIRL version (for example controlling a machine tool working on expensive materials).
\section{Quality criterion}

Figure \ref{fig:A} and \ref{fig:B} illustrate the difficulty of choosing the quality criterion. These plots show four different quality ciretria during a run of mc\_ANIRL and several runs of lstd\_ANIRL, for which the abscissa can not be the number of iterations.\\

The $||\mu(s_0) - \mu_E(s_0)||_2$ term is widely discussed in \citep{abbeel2004apprenticeship}'s additional material. It bears an interesting relation with the difference between the expert's value function and the current value function with respect \emph{to the current reward} (equation \ref{eqn:vmu}).\\

The fact that  the curves of  $||\mu(s_0) - \mu_E(s_0)||_2$ and $||\hat\mu(s_0) - \hat\mu_E(s_0)||_2$ are indistinguishable in figure \ref{fig:A} means that for it has access to a cheap simulator, mc\_ANIRL is as if it worked within an analitycal framework. This however can not be said of lstd\_ANIRL, for which the two curves are indeed different (Figure \ref{fig:B}). Not knowing the true value of $\mu_E(s_0)$ may be a problem for lstd\_ANIRL, as it can introduce an error int the halt criterion of the algorithm, $t = ||\bar\mu-\hat\mu_E(s_0)||$. After the algorithm has converged (it systematically does after only one iteration, this is being investigated), there is no way to know whether the policy is actually good or not.\\

It shall be noted that although it plays its role, the halt criterion is not a good measure of the quality of the current policy in mc\_ANIRL either, as it can be low when the policy is bad. The best policy, however, can be easily chosen from the $||\mu(s_0) - \mu_E(s_0)||_2$ term, which mc\_ANIRL can compute. When this term is low, the objective performance (that is, $V^E(s_0)-V^\pi(s_0)$ with respect to the unknow true reward function) is low too. 
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_e.pdf}
\caption{$||\mu_E(s_0)-\mu_\pi(s_0)||_2$ with respect to the number of samples available from the expert. Our algorithm is not as good as \citet{abbeel2004apprenticeship} with very few samples, but make up for it very soon.}
\label{fig:E}
\end{figure}
\label{sec:perf}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_a.pdf}
\caption{Different criteria with respect to the number of iterations for a run of mc\_ANIRL.}
\label{fig:A}
\end{figure}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_b.pdf}
\caption{Different criteria with respect to the number of samples from the expert, for several runs of lstd\_ANIRL.}
\label{fig:B}
\end{figure}
\section{Conclusion}
\label{sec:conclusion}
\bibliographystyle{named}
\bibliography{../Biblio/Biblio}
\end{document}

>>>>

\section{Background}
\label{sec:back}
A sequential decision problem is often framed as a Markov Decision
Process (MDP)~\citep{puterman1994markov}. A MDP is a tuple
$\{S,A,P,R,\gamma\}$ with $S$ being the state space, $A$ the action
space, $P\in\mathcal{P}(S)^{S\times A}$ the set of Markovian
transition probabilities, $R\in\mathbb{R}^S$ the reward function
(assumed to be absolutely bounded by 1) and $\gamma\in[0,1[$ a
discounting factor. A policy $\pi\in A^S$ maps states to action. The
quality of a policy is quantified by the associated value function
$V^\pi$, which associates to each state the expected and discounted
cumulative reward:
\begin{equation}
  V^\pi(s) = E[\sum_{t=0}^\infty \gamma^t R(s_t)|s_0=s, \pi]
\end{equation}
Dynamic programming aims at finding the optimal policy $\pi^*$, that
is one of the policies associated to the optimal value function,
$V^* = \argmax_\pi V^\pi$, which maximizes the value for each state.
If the model (that is transition probabilities and the reward
function) is unknown, learning the optimal control through
interactions is addressed by reinforcement learning.

@@

We assume that the true reward function belongs to some hypothesis
space $\mathcal{H}_\phi = \{\theta^T \phi(s),
\theta\in\mathbb{R}^p\}$, of which we assume the basis functions to
be bounded by 1: $|\phi_i(s)|\leq 1, \forall s\in S, 1\leq i \leq
p$. Therefore, there exists a parameter vector $\theta^*$ such that:
\begin{equation}
  R^*(s) = (\theta^*)^T \phi(s)
\end{equation}
In order to ensure that rewards are bounded, we impose that
$\|\theta\|_2\leq 1$. For any reward function belonging to
$\mathcal{H}_\phi$ and for any policy $\pi$, the related value
function $V^\pi(s)$ can be expressed as follows:
\begin{align}
  V^\pi(s) &= E[\sum_{t=0}^\infty \gamma^t \theta^T \phi(s_t)|s_0=s, \pi]
  \\
  &= \theta^T  E[\sum_{t=0}^\infty \gamma^t \phi(s_t)|s_0=s, \pi]
\end{align}
Therefore, the value function is also linearly parameterized, with
the same weights and with basis functions being grouped into the
so-called \emph{feature expectation} $\mu^\pi$:
\begin{equation}
  \mu^\pi(s) = E[\sum_{t=0}^\infty \gamma^t \phi(s_t)|s_0=s, \pi]
\end{equation}
Recall that the problem is to find a policy whose performance is
close to that of the expert's for the starting state $s_0$, on the
unknown reward function $R^*$. In order to achieve this goal, it is
proposed in~\citep{abbeel2004apprenticeship} to find a policy $\tilde{\pi}$ such
that $\|\mu^{\pi_E}(s_0)-\mu^{\tilde{\pi}}(s_0)\|_2\leq \epsilon$
for some (small) $\epsilon>0$. Actually, this ensures that the value
of the expert's policy and the value of the estimated policy (for
the starting state $s_0$) are close for \emph{any} reward function
of $\mathcal{H}_\phi$:
\begin{align}
  |V^{\pi_E}(s_0) - V^{\tilde{\pi}}(s_0)| &=
  |\theta^T(\mu^{\pi_E}(s_0)-\mu^{\tilde{\pi}}(s_0))|
  \label{eqn:vs0}
  \\
  &\leq \|\mu^{\pi_E}(s_0)-\mu^{\tilde{\pi}}(s_0)\|_2
\end{align}
This last equation uses the Cauchy-Schwartz inequality and the
assumption that $\|\theta\|_2\leq 1$. Therefore, the approach
described here does not ensure to retrieve the true reward function
$R^*$, but to act as well as the expert under this reward function
(and actually under any reward function, notably the unknown optimal
one).

@@

\section{LSTD-$\mu$}
Let us write the definition of the $i^\text{th}$ component of a
feature expectation $\mu^\pi(s)$ for some policy $\pi$:
\begin{equation}
  \mu_i^\pi(s) = E[\sum_{t=0}^\infty \gamma^t \phi_i(s_t)|s_0=s,\pi]
  \label{eqn:phi}
\end{equation}
This is exactly the definition of the value function of the policy
$\pi$ for the MDP considered with the $i^\text{th}$ basis function
$\phi_i(s)$ as the reward function. There exists many algorithms to
estimate a value function, any of them can be used to estimate
$\mu_i^\pi$. Based on this remark, we propose to use specifically
the least-squares temporal difference (LSTD)
algorithm~\citep{bradtke1996linear} to estimate each component of the
feature expectation (as each of these components can be understood
as a value function related to a specific and known reward
function).

Assume that a set of transitions $\{(s_t,r_t,s_{t+1})_{1\leq t \leq
n}\}$ sampled according to the policy $\pi$ is available. We assume
that value functions are searched for in some  hypothesis space
$\mathcal{H}_\psi = \{ \hat{V}_\xi(s) = \sum_{i=1}^q \xi_i \psi_i(s)
= \xi^T \psi(s), \xi\in\mathbb{R}^q\}$. As reward and value
functions are possibly quite different, another hypothesis space is
considered for value function estimation. But if $\mathcal{H}_\phi$
is rich enough, one can still consider
$\mathcal{H}_\psi=\mathcal{H}_\phi$. Therefore, we are looking for
an approximation of the following form:
\begin{equation}
  \hat{\mu}_i^\pi(s) = (\xi_i^*)^T \psi(s)
  \label{eqn:psi}
\end{equation}
The parameter vector $\xi_i^*$ is here the LSTD estimate:
\begin{equation}
  \xi_i^* = \left(\sum_{t=1}^n
  \psi(s_t)(\psi(s_t)-\gamma\psi(s'_{t}))^T\right)^{-1}
  \sum_{t=1}^n \psi(s_t) \phi_i(s_t)
\end{equation}
For apprenticeship learning, we are interested more particularly in
$\hat{\mu}^\pi(s_0)$. Let $\Psi = (\psi_i(s_t))_{t,i}$ be the
$n\times q$ matrix of values predictors, $\Delta\Psi = (\psi_i(s_t)
- \gamma\psi_i(s'_t))_{t,i}$ be the related $n\times q$ matrix and
$\Phi = (\phi_i(s_t))_{t,i}$ the $n\times p$ matrix of reward
predictors. It can be easily checked that $\hat{\mu}^\pi(s_0)$
satisfies:
\begin{equation}
  (\hat{\mu}^\pi(s_0))^T = \psi(s_0)^T (\Psi^T \Delta\Psi)^{-1} \Psi^T \Phi
\end{equation}
This provides an efficient way to estimate the feature expectation
of the expert in $s_0$.

@@

\section{Experimental benchmark}
\label{sec:exp}
\subsection{Experiment description and results}
The experimental benchmark chosen here is the same as in \citep{ng2000algorithms}, a 5x5 grid world. The agent is in one of the case of the grid (whose coordinates is the state) and can choose at each step one of the four compass directions (the action). With probability 0.9, the agent moves in the intended direction. With probability 0.1, the direction is randomly drawn (and thus have probability 0.25 to match the original direction). The reward optimized by the expert is 0 everywhere but in the upper-right square, where it is 1. For every policy, an episode ends when the upper right square is attained, or after 20 steps. At the start of each episode, the agent is in the lower-left corner of the grid (the opposite of where the reward is).\\

Both the state and action spaces are finite and of small cardinality. Hence, the chosen feature functions $\phi$ and $\psi$ (see equations \ref{eqn:phi} and \ref{eqn:psi} for a remainder of their meaning) are the typical features of a tabular representation : 0 everywhere but at a given index $i$ for which the value is 1. There is a bijective mapping from the input space elements to the indexes $i$ for which the coordinate of the feature is 1.\\

Both \citet{abbeel2004apprenticeship}'s algorithm (mc\_ANIRL) and our adaptation (lstd\_ANIRL) are tested side by side. The MDP solver of mc\_ANIRL is LSPI with a (very) big matrix $D$ as a sample source. $\mu_\pi(s_0)$ and $\mu_E(s_0)$ are computed thanks to a (very) big Monte-Carlo estimation. Both these computations are  as good as perfect theoretical solvers for all intended purpose on this toy problem. We thus are in the case intended by \citet{abbeel2004apprenticeship}.\\
On the other hand lstd\_ANIRL is used as if it could not have access to the simulator. It uses LSPI and LSTD$\mu$, fed only with the expert's transitions. This corresponds to a real-life setting where data generation is expensive and the system can not be controlled by an untrained machine.\\

We want to compare the porformance of both versions of the algorithm with repect to the number of samples available from the expert, as these samples usually are the bottleneck. The discussion about the choice of the performance metric has its own dedicated subsection (subsection \ref{sec:perf}). We use here the $||\mu(s_0) - \mu_E(s_0)||_2$ error term.\\

Figure \ref{fig:E} shows, for some numbers of samples from the expert, the value of $||\mu(s_0)-\mu_E(s_0)||_2$ after the algorithm converged or attained the maximum number of iterations (we used 40). The best policy is found by lstd\_ANIRL after one iteration only\footnote{Precise reasons for what it happens are not clear now, but certainly have something to do with the fact that all the estimations are made along the same distribution of samples.} whereas in mc\_ANIRL convergence happens after at least ten iterations and the best policy is not always the last. The score of the best policy (not the last) is what is plotted here.\\

We can see that although lstd\_ANIRL is not as good as mc\_ANIRL when very few samples are available, both algorithm quickly converge to almost the same value (we don't know yet if the seemingly slightly better performance of lstd\_ANIRL is an artifact). The fact that lstd\_ANIRL can work in a batch, off-policy and model-free setting, while requesting less computing power than mc\_ANIRL makes it suitable to a range of task inaccessible to the mc\_ANIRL version (for example controlling a machine tool working on expensive materials).
\subsection{Discussion about the quality criterion}
Figure \ref{fig:A} and \ref{fig:B} illustrate the difficulty of choosing the quality criterion. These plots show four different quality ciretria during a run of mc\_ANIRL and several runs of lstd\_ANIRL, for which the abscissa can not be the number of iterations.\\

The $||\mu(s_0) - \mu_E(s_0)||_2$ term is widely discussed in \citep{abbeel2004apprenticeship}'s additional material. It bears an interesting relation with the difference between the expert's value function and the current value function in the initial state with respect \emph{to the current reward} (equation \ref{eqn:vs0}).\\

The fact that  the curves of  $||\mu(s_0) - \mu_E(s_0)||_2$ and $||\hat\mu(s_0) - \hat\mu_E(s_0)||_2$ are indistinguishable in figure \ref{fig:A} means that for it has access to a cheap simulator, mc\_ANIRL is as if it worked within an analitycal framework. This however can not be said of lstd\_ANIRL, for which the two curves are indeed different (Figure \ref{fig:B}). Not knowing the true value of $\mu_E(s_0)$ may be a problem for lstd\_ANIRL, as it can introduce an error int the halt criterion of the algorithm\footnote{This equation differs from what has been given as the second step of the algorithm in section \ref{sec:back}. This is because we implemented the version of the algorithm that uses a projection (see \citet{abbeel2004apprenticeship}'s supplementary material for an in-depth discussion of both versions). Although the mathematical expressions are different, both convey the same meaning and are exchangeable.}, $t = ||\bar\mu-\hat\mu_E(s_0)||$. After the algorithm has converged there is no way to know whether the policy is actually good or not other than actually testing it.\\

It shall be noted that although it plays its role, the halt criterion is not a good measure of the quality of the current policy in mc\_ANIRL either, as it can be low when the policy is bad. The best policy, however, can be easily chosen from the $||\mu(s_0) - \mu_E(s_0)||_2$ term, which mc\_ANIRL can compute. When this term is low, the objective performance (that is, $V^E(s_0)-V^\pi(s_0)$ with respect to the unknow true reward function) is low too. 
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_e.pdf}
\caption{$||\mu_E(s_0)-\mu_\pi(s_0)||_2$ with respect to the number of samples available from the expert. Our algorithm is not as good as \citet{abbeel2004apprenticeship} with very few samples, but make up for it very soon.}
\label{fig:E}
\end{figure}
\label{sec:perf}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_a.pdf}
\caption{Different criteria with respect to the number of iterations for a run of mc\_ANIRL.}
\label{fig:A}
\end{figure}
\begin{figure}
\includegraphics[width=.5\textwidth]{../Code/courbe_b.pdf}
\caption{Different criteria with respect to the number of samples from the expert, for several runs of lstd\_ANIRL.}
\label{fig:B}
\end{figure}
\section{Conclusion}

\label{sec:conclusion}
\bibliographystyle{named}
\bibliography{../Biblio/Biblio}
\end{document}
